Viscous Erosion in Porous Media

### 2018-03-27 docs/methods/erosion_methods.tex
went through intro again

We validate our method on a single circular body placed symmetrically in
a pipe flow.  By artificially fixing the area of the body as a function
of time, we are able to characterize the long-time behavior of the shape
and the resulting flow and these results agree with analytical results.
Then, we compute the vorticity of erosion in multiply-connected
geometries to better characterize erosion in porous media. 
\todo[inline]{Bryan is here in editing}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Limitations}

We begin by making two fundamental design choices: first, we restrict
ourselves to two spatial dimensions, and second the bodies are
considered immobile (i.e.~fixed to their initial locations). The
restriction to two dimensions allows us to simulate the erosion of many bodies
(up to $50$ in this manuscript) with high resolution, giving us the
ability to accurately characterize the erosion of a porous medium. While
BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible. The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation. While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.

@@

To simulate multiple bodies, it is essential to resolve the nonlocal
effects between the different bodies.  In this work, these interactions
are included with high-order accuracy by using an integral equation
method~\cite{poz1992}.  Integral equations have been used extensively to
simulate viscous fluids in complex geometries, including porous media
flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}.  For nearly
touching bodies, the quadrature associated with discretizing a BIE can
lead to instabilities of specialized quadrature is not applied.  Since
our bodies do not move, we are able to use upsampling, but future work
will require a near-singular integration scheme~\cite{qua-bir2014a,
klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.

>>>>

We validate our method on a single circular body placed symmetrically in
a pipe flow.  By artificially fixing the area of the body as a function
of time, we are able to characterize the long-time behavior of the shape
and the resulting flow and these results agree with analytical results.
Then, we compute the vorticity of erosion in multiply-connected
geometries to better characterize erosion in porous media.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Limitations} 
We begin by making two fundamental design choices: first, we restrict ourselves to two spatial dimensions, and second the bodies are considered immobile (i.e.~fixed to their initial locations). The restriction to two dimensions allows us to simulate the erosion of many bodies (up to $50$ in this manuscript) with high resolution, giving us the ability to accurately characterize the erosion of a porous medium. While BIEs are available in three dimensions, the extra computational cost limits the number of bodies that could be practically simulated, making porous-medium simulations less feasible. The second assumption of immobile bodies affords a simple framework to study the effects of erosion in isolation. While other effects, such as sedimentation or transport, undoubtedly play a role in real applications, these effects would introduce additional complexity, both conceptually and numerically.

@@

To simulate multiple bodies, it is essential to resolve the nonlocal
effects between the different bodies.  In this work, these interactions
are included with high-order accuracy by using an integral equation
method~\cite{poz1992}.  Integral equations have been used extensively to
simulate viscous fluids in complex geometries, including porous media
flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2016}. Challenges of a
BIE formulation include resolving the interactions between nearly
touching bodies and developing efficient preconditioners for the
discretized system.  Possible preconditioners include
multigrid~\cite{qua-bir2015a} and the inverse fast multipole
method~\cite{qua-cou-dar2018}, but the results presented in this work
require no more than $\mathcal{O}(100)$ GMRES iterations which is too
small to make preconditioners for BIEs effective; preconditioners will
be considered further in future work when there are many more grains
that are also dynamic.  To address the nearly-singular integrands, we
take advantage of the fact that the grains are eroding and not moving,
so their separation increases with time.  Therefore, in this work, we
apply an upsampling scheme, but in future work, we will require a
near-singular integration scheme~\cite{qua-bir2014a,
klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.
